\documentclass[noauthor,noinstructornotes]{ximera}

\title{Week 14}
\author{Math 1193 Design Team}

\begin{document}
\begin{abstract}
    Activities for Week 14.
\end{abstract}
\maketitle

\begin{problem}
The king has decided to provide a family with rice for a month. 
On day 0, he gives them 1 grain of rice. On each subsequent day, 
he gives them 100\% more rice than the previous day. 

\begin{enumerate}
    \item On day 1, how much rice does the king give the family?
    \item What about on day 2?
    \item Day 12?
    \item Organize your information in a reasonable way.
    \item What is the role of exponentiation in this problem? Write down
    your answer in a sentence.
    \item Write down a function that takes a number of days \(x\)
    and returns the amount \(f(x)\) fo grains of rice the king gives the
    family on day \(x\).
\end{enumerate}
\end{problem}

\begin{problem}
The number of bacteria in a colony decreases by 5\% per day in certain conditions.

\begin{enumerate}
    \item If the colony starts with 10,000 bacteria, how many are left
    after 1 day in those conditions?
    \item How many are left after 2 days?
    \item 5 days?
    \item When will there be 5000 bacteria left in the colony?
\end{enumerate}

\begin{instructorNotes}
Perhaps some students may try to do this without an equation. Try 
prompting them to organize their work more on a sheet of paper.
Students need to practice writing, especially since that's what exams 
are like!
\end{instructorNotes}
\end{problem}

\end{document}
